Manuscript Figures for Genome Biology

### 2018-08-14 manuscript_figures/manuscript_figures.Rmd
Update manuscript figures to distinguish between yeast sim settings

```{r Figure2, fig.width = 10, fig.height = 8}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("yeast", objects) & 
                   grepl("de5", objects) & 
                  !grepl("uninf", objects)]

@@

```{r, fig.width = 10, fig.height = 4}
for (org in c("yeast", "polyester")){

@@

>>>>

```{r Figure2, fig.width = 10, fig.height = 8}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("yeast-", objects) & 
                   grepl("de5", objects) & 
                  !grepl("uninf", objects)]

@@

```{r, fig.width = 10, fig.height = 4}
for (org in c("yeast-", "polyester")){

@@

# remove simulation objects
sim <- unique(c(which(grepl("simulations", objects)),
               which(grepl("yeast-", objects)),
               which(grepl("polyester", objects))))
if (length(sim) > 0){
  objects <- objects[-sim]
}
